---
title: "AB 617"
author: "Brandyn Ruiz"
output: html_document
---

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
library(plotly)
library(scales)
library(leaflet)
library(sp)
library(sf)
library(rgdal)

```

```{r WCWLB Datasets, warning=FALSE, message=FALSE, echo=FALSE}
# Folders within WCWLB
folders <- list.files(path = paste0(getwd(), "/WCWLB"))

WCWLB <- tibble("Date/Time" = NA, "Value" = NA, "Unit" = NA, "Averaging Hour" = NA, Monitor = NA)%>%
  as.data.frame()

for (i in folders) {

  filepath <- list.files(path = paste0(getwd(), "/WCWLB/", i))
  for (j in filepath) {
    WCWLB <- rbind(WCWLB,
                   read_excel(paste0(getwd(), "/WCWLB/", i, "/", j), skip = 2)%>%
                     mutate(Monitor = i))
  }
}

WCWLB <- WCWLB%>%
  filter(complete.cases(.))%>%
  mutate(DateTime = as.POSIXct(`Date/Time`, format = "%m/%d/%Y %I:%M:%S %p", tz = Sys.timezone()),
         Pollutants = ifelse(Unit == "counts/cm3", "Ultrafine Particles",
                       ifelse(Unit == "ppb", "Hydrogen Sulfide",  "Black Carbon")),
         Boundary = "WCWLB")%>%
  select(Boundary, DateTime, Monitor, Value, Unit, Pollutants, `Averaging Hour`, `Date/Time`)%>%
  mutate_at("Value", as.numeric)%>%
  mutate(Value = round(Value, 2)) %>% 
    separate(`Date/Time`, into = c("Date", "Hour", "Time"), sep = "\\s")%>%
    mutate(Time = paste(Hour, Time, sep = " "),
           Date = as.Date(Date, format = "%m/%d/%Y")) %>% 
    select(-Hour)%>%
  mutate(Source = "WCWLB")

# write.csv(WCWLB, "WCWLB.csv", row.names = FALSE, na = "")

```

```{r SELA Dataset, warning=FALSE, message=FALSE, echo=FALSE}

# Folders within SELA
folders <- list.files(path = paste0(getwd(), "/SELA"))

SELA <- tibble("Date/Time" = NA, "Value" = NA, "Unit" = NA, "Averaging Hour" = NA, Monitor = NA)%>%
  as.data.frame()

for (i in folders) {

  filepath <- list.files(path = paste0(getwd(), "/SELA/", i))
  for (j in filepath) {
    SELA <- rbind(SELA,
                   read_excel(paste0(getwd(), "/SELA/", i, "/", j), skip = 2)%>%
                     mutate(Monitor = i))
  }
}

SELA <- SELA%>%
  filter(complete.cases(.))%>%
  mutate(DateTime = as.POSIXct(`Date/Time`, format = "%m/%d/%Y %I:%M:%S %p", tz = Sys.timezone()),
         Pollutants = ifelse(Unit == "counts/cm3", "Ultrafine Particles",
                       ifelse(Unit == "ppb", "Hydrogen Sulfide",  "Black Carbon")),
         Boundary = "SELA")%>%
  select(Boundary, DateTime, Monitor, Value, Unit, Pollutants, `Averaging Hour`, `Date/Time`)%>%
  mutate_at("Value", as.numeric)%>%
  mutate(Value = round(Value, 2)) %>% 
    separate(`Date/Time`, into = c("Date", "Hour", "Time"), sep = "\\s")%>%
    mutate(Time = paste(Hour, Time, sep = " "),
           Date = as.Date(Date, format = "%m/%d/%Y")) %>% 
    select(-Hour)%>%
  mutate(Source = "SELA")

# write.csv(SELA, "SELA.csv", row.names = FALSE, na = "")

```

```{r ELABHWC Dataset, warning=FALSE, message=FALSE, echo=FALSE}

# Folders within ELABHWC
folders <- list.files(path = paste0(getwd(), "/ELABHWC"))

ELABHWC <- tibble("Date/Time" = NA, "Value" = NA, "Unit" = NA, "Averaging Hour" = NA, Monitor = NA)%>%
  as.data.frame()

for (i in folders) {

  filepath <- list.files(path = paste0(getwd(), "/ELABHWC/", i))
  for (j in filepath) {
    ELABHWC <- rbind(ELABHWC,
                   read_excel(paste0(getwd(), "/ELABHWC/", i, "/", j), skip = 2)%>%
                     mutate(Monitor = i))
  }
}

ELABHWC <- ELABHWC%>%
  filter(complete.cases(.))%>%
  mutate(DateTime = as.POSIXct(`Date/Time`, format = "%m/%d/%Y %I:%M:%S %p", tz = Sys.timezone()),
         Pollutants = ifelse(Unit == "counts/cm3", "Ultrafine Particles",
                       ifelse(Unit == "ppb", "Hydrogen Sulfide",  "Black Carbon")),
         Boundary = "WCWLB")%>%
  select(Boundary, DateTime, Monitor, Value, Unit, Pollutants, `Averaging Hour`, `Date/Time`)%>%
  mutate_at("Value", as.numeric)%>%
  mutate(Value = round(Value, 2)) %>% 
    separate(`Date/Time`, into = c("Date", "Hour", "Time"), sep = "\\s")%>%
    mutate(Time = paste(Hour, Time, sep = " "),
           Date = as.Date(Date, format = "%m/%d/%Y")) %>% 
    select(-Hour)%>%
  mutate(Source = "ELABHWC")

# write.csv(ELABHWC, "ELABHWC.csv", row.names = FALSE, na = "")


```

```{r WCWLB Dashboards , warning=FALSE, message=FALSE, echo=FALSE}
# data dashboards that feature more in the past, first link featured more in the present

# WCWLB
## 710
filenames <- list.files(path = paste0(getwd(), "/Dashboard"),
                        pattern = "710+.*csv")

Dashboard_710 <- tibble("Hour of Date (LST)" = NA, "Pollutants" = NA, "Station" = NA, "Unit" = NA, "Avg. Value" = NA)%>%
  as.data.frame()

for (i in filenames) {
  Dashboard_710 <- rbind(Dashboard_710,
                         read_csv(paste0(getwd(), "/Dashboard/", i)))
} 

Dashboard_710$Station <- "710"

Dashboard_710 <- Dashboard_710%>%
  filter(complete.cases(.)) %>% 
  mutate_at("Avg. Value", as.numeric) %>%
  mutate("Avg. Value" = ifelse(Unit == "ng/m³", `Avg. Value` * 10^-3,
                               ifelse(Unit == "Counts/cm³ x 1000", `Avg. Value` * 1000, `Avg. Value`)),
         Unit = gsub("ng/m³", "μg/m3", Unit),
         Unit = gsub("Counts/cm³ x 1000", "counts/cm3", Unit)) %>% 
  rename("Date/Time" = `Hour of Date (LST)`, "Monitor"  = Station, "Value" = `Avg. Value`)%>%
    mutate(`Date/Time` = as.POSIXct(`Date/Time`, format = "%B %d, %Y, %I %p"))%>%
    separate(`Date/Time`, into = c("Date", "Time"), sep = "\\s", remove = FALSE)%>%
    mutate(Date = as.Date(Date, format = "%Y-%m-%d"),
           Time = gsub(":.*", "", Time)) %>% 
    mutate_at("Time", as.numeric)%>%
    mutate(Time = ifelse(Time > 11, paste(Time, "PM", sep = " "), paste(Time, "AM", sep = " ")))%>%
    separate(Time, into = c("Hour", "Time"), sep = "\\s") %>% 
    mutate_at("Hour", as.numeric)%>%
    mutate(Hour = ifelse(Hour == 0, 12,
                         ifelse(Hour > 12, Hour - 12, Hour)),
           Hour = paste0(Hour, ":00:00 ", Time)) %>%
    select(-Time)%>%
  mutate(Value = round(Value, 2),
         Source = "Dashboard",
         DateTime = as.POSIXct(`Date/Time`, format = "%m/%d/%Y %I:%M:%S %p", tz = Sys.timezone()),
         Pollutants = gsub("Black carbon", "Black Carbon", Pollutants),
         Pollutants = gsub("Ultrafine particles", "Ultrafine Particles", Pollutants))%>%
  select(-`Date/Time`) %>% 
  rename("Time" = Hour)

## Hudson
filenames <- list.files(path = paste0(getwd(), "/Dashboard"),
                        pattern = "Hudson_+.*csv")

Dashboard_Hudson <- tibble("Hour of Date (LST)" = NA, "Pollutants" = NA, "Station" = NA, "Unit" = NA, "Avg. Value" = NA)%>%
  as.data.frame()

for (i in filenames) {
  Dashboard_Hudson <- rbind(Dashboard_Hudson,
                         read_csv(paste0(getwd(), "/Dashboard/", i)))
} 

Dashboard_Hudson$Station <- "Hudson"

Dashboard_Hudson <- Dashboard_Hudson%>%
  filter(complete.cases(.)) %>% 
  mutate_at("Avg. Value", as.numeric) %>%
  mutate("Avg. Value" = ifelse(Unit == "ng/m³", `Avg. Value` * 10^-3,
                               ifelse(Unit == "Counts/cm³ x 1000", `Avg. Value` * 1000, `Avg. Value`)),
         Unit = gsub("ng/m³", "μg/m3", Unit),
         Unit = gsub("Counts/cm³ x 1000", "counts/cm3", Unit)) %>% 
  rename("Date/Time" = `Hour of Date (LST)`, "Monitor"  = Station, "Value" = `Avg. Value`)%>%
    mutate(`Date/Time` = as.POSIXct(`Date/Time`, format = "%B %d, %Y, %I %p"))%>%
    separate(`Date/Time`, into = c("Date", "Time"), sep = "\\s", remove = FALSE)%>%
    mutate(Date = as.Date(Date, format = "%Y-%m-%d"),
           Time = gsub(":.*", "", Time)) %>% 
    mutate_at("Time", as.numeric)%>%
    mutate(Time = ifelse(Time > 11, paste(Time, "PM", sep = " "), paste(Time, "AM", sep = " ")))%>%
    separate(Time, into = c("Hour", "Time"), sep = "\\s") %>% 
    mutate_at("Hour", as.numeric)%>%
    mutate(Hour = ifelse(Hour == 0, 12,
                         ifelse(Hour > 12, Hour - 12, Hour)),
           Hour = paste0(Hour, ":00:00 ", Time)) %>%
    select(-Time)%>%
  mutate(Value = round(Value, 2),
         Source = "Dashboard",
         DateTime = as.POSIXct(`Date/Time`, format = "%m/%d/%Y %I:%M:%S %p", tz = Sys.timezone()),
         Pollutants = gsub("Black carbon", "Black Carbon", Pollutants),
         Pollutants = gsub("Ultrafine particles", "Ultrafine Particles", Pollutants),
         Pollutants = gsub("Hydrogen sulfide", "Hydrogen Sulfide", Pollutants))%>%
  select(-`Date/Time`) %>% 
  rename("Time" = Hour)

```

```{r ELABHWC Dashboards, warning=FALSE, message=FALSE, echo=FALSE}
# ELABHWC

## Central LA
filenames <- list.files(path = paste0(getwd(), "/Dashboard"),
                        pattern = "CentralLA+.*csv")

Dashboard_CentralLA <- tibble("Hour of Date (LST)" = NA, "Pollutants" = NA, "Station" = NA,
                              "Unit" = NA, "Avg. Value" = NA)%>%
  as.data.frame()

for (i in filenames) {
  Dashboard_CentralLA <- rbind(Dashboard_CentralLA,
                         read_csv(paste0(getwd(), "/Dashboard/", i)))
} 

Dashboard_CentralLA$Station <- "CentralLA"

Dashboard_CentralLA <- Dashboard_CentralLA%>%
  filter(complete.cases(.)) %>% 
  mutate_at("Avg. Value", as.numeric) %>%
  mutate("Avg. Value" = ifelse(Unit == "ng/m³", `Avg. Value` * 10^-3,
                               ifelse(Unit == "Counts/cm³ x 1000", `Avg. Value` * 1000, `Avg. Value`)),
         Unit = gsub("ng/m³", "μg/m3", Unit),
         Unit = gsub("Counts/cm³ x 1000", "counts/cm3", Unit)) %>% 
  rename("Date/Time" = `Hour of Date (LST)`, "Monitor"  = Station, "Value" = `Avg. Value`)%>%
    mutate(`Date/Time` = as.POSIXct(`Date/Time`, format = "%B %d, %Y, %I %p"))%>%
    separate(`Date/Time`, into = c("Date", "Time"), sep = "\\s", remove = FALSE)%>%
    mutate(Date = as.Date(Date, format = "%Y-%m-%d"),
           Time = gsub(":.*", "", Time)) %>% 
    mutate_at("Time", as.numeric)%>%
    mutate(Time = ifelse(Time > 11, paste(Time, "PM", sep = " "), paste(Time, "AM", sep = " ")))%>%
    separate(Time, into = c("Hour", "Time"), sep = "\\s") %>% 
    mutate_at("Hour", as.numeric)%>%
    mutate(Hour = ifelse(Hour == 0, 12,
                         ifelse(Hour > 12, Hour - 12, Hour)),
           Hour = paste0(Hour, ":00:00 ", Time)) %>%
    select(-Time)%>%
  mutate(Value = round(Value, 2),
         Source = "Dashboard",
         DateTime = as.POSIXct(`Date/Time`, format = "%m/%d/%Y %I:%M:%S %p", tz = Sys.timezone()),
         Pollutants = gsub("Black carbon", "Black Carbon", Pollutants),
         Pollutants = gsub("Ultrafine particles", "Ultrafine Particles", Pollutants))%>%
  select(-`Date/Time`) %>% 
  rename("Time" = Hour)

## Resurrection Church
filenames <- list.files(path = paste0(getwd(), "/Dashboard"),
                        pattern = "ResurrectionChurch_+.*csv")

Dashboard_ResurrectionChurch <- tibble("Hour of Date (LST)" = NA, "Pollutants" = NA, "Station" = NA,
                              "Unit" = NA, "Avg. Value" = NA)%>%
  as.data.frame()

for (i in filenames) {
  Dashboard_ResurrectionChurch <- rbind(Dashboard_ResurrectionChurch,
                         read_csv(paste0(getwd(), "/Dashboard/", i)))
} 

Dashboard_ResurrectionChurch$Station <- "ResurrectionChurch"

Dashboard_ResurrectionChurch <- Dashboard_ResurrectionChurch%>%
  filter(complete.cases(.)) %>% 
  mutate_at("Avg. Value", as.numeric) %>%
  mutate("Avg. Value" = ifelse(Unit == "ng/m³", `Avg. Value` * 10^-3,
                               ifelse(Unit == "Counts/cm³ x 1000", `Avg. Value` * 1000, `Avg. Value`)),
         Unit = gsub("ng/m³", "μg/m3", Unit),
         Unit = gsub("Counts/cm³ x 1000", "counts/cm3", Unit)) %>% 
  rename("Date/Time" = `Hour of Date (LST)`, "Monitor"  = Station, "Value" = `Avg. Value`)%>%
    mutate(`Date/Time` = as.POSIXct(`Date/Time`, format = "%B %d, %Y, %I %p"))%>%
    separate(`Date/Time`, into = c("Date", "Time"), sep = "\\s", remove = FALSE)%>%
    mutate(Date = as.Date(Date, format = "%Y-%m-%d"),
           Time = gsub(":.*", "", Time)) %>% 
    mutate_at("Time", as.numeric)%>%
    mutate(Time = ifelse(Time > 11, paste(Time, "PM", sep = " "), paste(Time, "AM", sep = " ")))%>%
    separate(Time, into = c("Hour", "Time"), sep = "\\s") %>% 
    mutate_at("Hour", as.numeric)%>%
    mutate(Hour = ifelse(Hour == 0, 12,
                         ifelse(Hour > 12, Hour - 12, Hour)),
           Hour = paste0(Hour, ":00:00 ", Time)) %>%
    select(-Time)%>%
  mutate(Value = round(Value, 2),
         Source = "Dashboard",
         DateTime = as.POSIXct(`Date/Time`, format = "%m/%d/%Y %I:%M:%S %p", tz = Sys.timezone()),
         Pollutants = gsub("Black carbon", "Black Carbon", Pollutants),
         Pollutants = gsub("Ultrafine particles", "Ultrafine Particles", Pollutants),
         Pollutants = gsub("Hydrogen sulfide", "Hydrogen Sulfide", Pollutants))%>%
  select(-`Date/Time`) %>% 
  rename("Time" = Hour)


```

```{r Sources Merged, warning=FALSE, message=FALSE, echo=FALSE}
# WCWLB and Dashboard sources merged
 merged_710 <- rbind(Dashboard_710 %>% 
          select(-Unit),
      WCWLB%>%
          select(-c(Boundary, Unit, `Averaging Hour`)))%>%
    arrange(Date, Time) %>%
    mutate(dups = duplicated(across(-Source)))%>%
    filter(dups != TRUE)%>%
    select(-dups)

Hudson_merged <- rbind(Dashboard_Hudson %>% 
          select(-Unit),
      WCWLB%>%
          select(-c(Boundary, Unit, `Averaging Hour`)))%>%
    arrange(Date, Time) %>%
    mutate(dups = duplicated(across(-Source))) %>% 
    filter(dups != TRUE) %>% 
    select(-dups)

WCWLB_merged <- rbind(merged_710, Hudson_merged) %>% 
    mutate(dups = duplicated(.)) %>% 
    arrange(Date, Time) %>%
    filter(dups != TRUE) %>% 
    select(-dups)

# write.csv(WCWLB_merged, "WCWLB_merged.csv", row.names = FALSE)

##
CentralLA_merged <- rbind(Dashboard_CentralLA %>% 
          select(-Unit),
      ELABHWC%>%
          select(-c(Boundary, Unit, `Averaging Hour`)))%>%
    arrange(Date, Time) %>%
    mutate(dups = duplicated(across(-Source)))%>%
    filter(dups != TRUE) %>%
    select(-dups)

ResurrectionChurch_merged <- rbind(Dashboard_ResurrectionChurch %>% 
          select(-Unit),
      ELABHWC%>%
          select(-c(Boundary, Unit, `Averaging Hour`)))%>%
    arrange(Date, Time) %>%
    mutate(dups = duplicated(across(-Source))) %>% 
    filter(dups != TRUE) %>% 
    select(-dups)

ELABHWC_merged <- rbind(CentralLA_merged, ResurrectionChurch_merged) %>% 
    mutate(dups = duplicated(.)) %>% 
    arrange(Date, Time) %>% 
    filter(dups != TRUE) %>% 
    select(-dups)

# write.csv(ELABHWC_merged, "ELABHWC_merged.csv", row.names = FALSE)

```

```{r Air Monitor Geocodes, warning=FALSE, message=FALSE, echo=FALSE}
AirMonitors <- read_excel("AirMonitors.xlsx")

# WCWLB_merged <- merge(WCWLB_merged, AirMonitors %>% 
#           select(-Boundary))
# # write.csv(WCWLB_merged, "WCWLB_merged.csv", row.names = FALSE)
# 
# SELA <- merge(SELA, AirMonitors %>% 
#                 select(-Boundary))
# # write.csv(SELA, "SELA.csv", row.names = FALSE)
# 
# ELABHWC_merged <- merge(ELABHWC_merged, AirMonitors %>% 
#                           select(-Boundary))
# # write.csv(ELABHWC_merged, "ELABHWC_merged.csv", row.names = FALSE)

```

## AB 617 Air Monitors
```{r AB617 Map, echo=FALSE, message=FALSE, warning=FALSE}
# AirMonitors <- read_excel("AirMonitors.xlsx")

AirMonitors <- AirMonitors %>% 
  mutate(Group = ifelse(Boundary == "WCWLB", "green",
                        ifelse(Boundary == "SELA", "orange", "red")))

markers <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = AirMonitors$Group
)

ELABHWC_shp <- readOGR(paste0(getwd(), "/AB617 Air Monitors/shp/ELABHWC.shp"), verbose = FALSE)
ELABHWC_shp <- spTransform(ELABHWC_shp, CRS("+proj=longlat +datum=WGS84 +no_defs"))

WCWLB_shp <- readOGR(paste0(getwd(), "/AB617 Air Monitors/shp/WCWLB.shp"), verbose = FALSE)
WCWLB_shp <- spTransform(WCWLB_shp, CRS("+proj=longlat +datum=WGS84 +no_defs"))

SELA_shp <- readOGR(paste0(getwd(), "/AB617 Air Monitors/shp/SELA.shp"), verbose = FALSE)
SELA_shp <- spTransform(SELA_shp, CRS("+proj=longlat +datum=WGS84 +no_defs"))


leaflet(AirMonitors) %>%
  addTiles() %>%
  addAwesomeMarkers(lng = ~Lon, lat= ~Lat, icon=~markers, label=~as.character(Monitor)) %>% 
  addPolygons(data=ELABHWC_shp,weight=5,col = 'grey50',
              popup = ~as.character("East Los Angeles, Boyle Heights, West Commerce"),
              label = ~~as.character("East Los Angeles, Boyle Heights, West Commerce"))%>% 
  addPolygons(data=WCWLB_shp,weight=5,col = 'grey50',
              popup = ~as.character("Wilmington Carson West Long Beach"),
              label = ~as.character("Wilmington Carson West Long Beach"))%>% 
  addPolygons(data=SELA_shp,weight=5,col = 'grey50',
              popup = ~as.character("Southeast Los Angeles (SELA) Emission Boundary"),
              label = ~as.character("Southeast Los Angeles (SELA) Emission Boundary"))

```

<br>

## WCWLB  Black Carbon Plots {.tabset}

### Hourly Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
# Hourly Averages
ggplotly(WCWLB_merged %>% 
             filter(Pollutants == "Black Carbon") %>% 
             ggplot(aes(x = DateTime, y = Value, group = Monitor, color = Monitor))+ 
             geom_line()+
             labs(x = "Date", y = "Concentration", title = "WCWLB Hourly Averages for Black Carbon")+
             theme(plot.title = element_text(hjust = 0.5)))

# Comparison between monitors
# ggplotly(WCWLB_merged %>% 
#     filter(Pollutants == "Black Carbon") %>% 
#     ggplot(aes(x = Monitor, y = Value, color = Monitor))+
#     geom_boxplot()+
#     coord_flip()+
#     labs(x = "", title = "Hourly Averages Between Monitors")+
#     theme(plot.title = element_text(hjust = 0.5)))
```

### Daily Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
# Daily Averages
ggplotly(WCWLB_merged %>% 
    filter(Pollutants == "Black Carbon") %>% 
    group_by(Monitor, Date) %>% 
    summarize(Avg = mean(Value)) %>% 
    arrange(Date, .by_group = TRUE) %>%
    ggplot(aes(x = Date, y = Avg, color = Monitor))+
    geom_line()+
    ggtitle("WCWLB Day Averages for Black Carbon")+
    theme(plot.title = element_text(hjust = 0.5)))

# Comparison between monitors
# ggplotly(WCWLB_merged %>% 
#     filter(Pollutants == "Black Carbon") %>% 
#     group_by(Monitor, Date) %>% 
#     summarize(Avg = mean(Value)) %>% 
#     arrange(Date, .by_group = TRUE) %>%
#     ggplot(aes(x = Monitor, y = Avg, color = Monitor))+
#     geom_boxplot()+
#     labs(x = "", title = "Daily Averages Between Monitors")+
#     coord_flip()+
#     theme(plot.title = element_text(hjust = 0.5)))
```

### Monthly Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
# Monthly Averages
ggplotly(WCWLB_merged %>% 
    filter(Pollutants == "Black Carbon") %>%
    mutate(Year = year(Date), Month = month(Date)) %>% 
    mutate(DateTime = my(paste0(Month, '/', Year))) %>% 
    group_by(Monitor, DateTime) %>% 
    summarize(Avg = mean(Value, na.rm = TRUE)) %>%
    ggplot(aes(x = DateTime, y = Avg, color = Monitor))+
    geom_line()+
    labs(title = "WCWLB Monthly Averages for Black Carbon")+
    theme(plot.title = element_text(hjust = 0.5)))

# Comparison between monitors
# ggplotly(WCWLB_merged %>% 
#     filter(Pollutants == "Black Carbon") %>%
#     mutate(Year = year(Date), Month = month(Date)) %>% 
#     mutate(DateTime = my(paste0(Month, '/', Year))) %>% 
#     group_by(Monitor, DateTime) %>% 
#     summarize(Avg = mean(Value, na.rm = TRUE)) %>%
#     ggplot(aes(x = Monitor, y = Avg, color = Monitor))+
#     geom_boxplot()+
#     labs(title = "Monthly Averages Between Monitors")+
#     theme(plot.title = element_text(hjust = 0.5)))

```

## {-}

## WCWLB Ultrafine Particle Plots {.tabset}

### Hourly Averages
```{r message=FALSE, warning=FALSE, echo=FALSE}
# Hourly averages
ggplotly(WCWLB_merged %>% 
    filter(Pollutants == "Ultrafine Particles") %>% 
    ggplot(aes(x = DateTime, y = Value, color = Monitor))+
    geom_line()+
    scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                  labels = trans_format("log10", math_format(10^.x)))+
    labs(x = "Date", title = "WCWLB Hourly Averages for Ultrafine Particles")+
    theme(plot.title = element_text(hjust = 0.5)))%>%
    layout(yaxis = list(ticktext = c(TeX("$10^{0}$"), TeX("$10^{2}$"), TeX("$10^{4}$"),
                                     TeX("$10^{6}$")),
                        tickfont = list(size = 15))) %>%
    config(mathjax = "cdn")

# Comparison between
# ggplotly(WCWLB_merged %>% 
#     filter(Pollutants == "Ultrafine Particles") %>% 
#     ggplot(aes(x = Monitor, y = Value, color = Monitor))+
#     geom_boxplot()+
#     labs(title = "Hourly Averages Between Monitors")+
#     theme(plot.title = element_text(hjust = 0.5)))
```

### Daily Averages
```{r message=FALSE, warning=FALSE, echo=FALSE}
# Daily Averages
ggplotly(WCWLB_merged %>% 
             filter(Pollutants == "Ultrafine Particles") %>% 
             group_by(Monitor, Date) %>% 
             summarize(Avg = mean(Value, na.rm = TRUE)) %>% 
             arrange(Date, .by_group = TRUE) %>%
             ggplot(aes(x = Date, y = Avg, color = Monitor))+
             geom_line()+
               scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                  labels = trans_format("log10", math_format(10^.x)))+
            # scale_y_continuous(labels = function(x) format(x, scientific = TRUE))+
             ggtitle("WCWLB Day Averages for Ultrafine Particles")+
             theme(plot.title = element_text(hjust = 0.5))) %>% 
  layout(yaxis = list(ticktext = c(TeX("$10^{0}$"), TeX("$10^{2}$"), TeX("$10^{4}$"),
                                     TeX("$10^{6}$")),
                        tickfont = list(size = 15))) %>%
    config(mathjax = "cdn")

# comparison between
# WCWLB_merged %>% 
#              filter(Pollutants == "Ultrafine Particles") %>% 
#              group_by(Monitor, Date) %>% 
#              summarize(Avg = mean(Value, na.rm = TRUE)) %>% 
#              arrange(Date, .by_group = TRUE) %>%
#              ggplot(aes(x = Monitor, y = Avg, color = Monitor))+
#              geom_boxplot()+
#             scale_y_continuous(labels = function(x) format(x, scientific = TRUE))+
#              ggtitle("Day Averages Between Monitors")+
#              theme(plot.title = element_text(hjust = 0.5))
```

### Monthly Averages
```{r message=FALSE, warning=FALSE, echo=FALSE}
# scientific_10 <- function(x) {
#   parse(text=gsub("e+", " %*% 10^", scales::scientific_format()(x)))
# }

# Monthly Averages
ggplotly(WCWLB_merged %>% 
             filter(Pollutants == "Ultrafine Particles") %>%
             mutate(Year = year(Date), Month = month(Date)) %>% 
             mutate(DateTime = my(paste0(Month, '/', Year))) %>% 
             group_by(Monitor, DateTime) %>% 
             summarize(Avg = mean(Value, na.rm = TRUE)) %>%
             ggplot(aes(x = DateTime, y = Avg, color = Monitor))+
             geom_line()+
             labs(title = "WCWLB Monthly Averages for Ultrafine Particles")+
           # scale_y_continuous(labels = function(x) format(x, scientific = TRUE))+

           scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                  labels = trans_format("log10", math_format(10^.x)))+
             theme(plot.title = element_text(hjust = 0.5))) %>% 
    layout(yaxis = list(ticktext = c(TeX("$10^{4.2}$"), TeX("$10^{4.4}$"), TeX("$10^{4.6}$"),
                                     TeX("$10^{4.8}$"), TeX("$10^{5}$")),
                        tickfont = list(size = 15))) %>% 
    config(mathjax = "cdn")
    
# Comparison between
# ggplotly(WCWLB_merged %>% 
#              filter(Pollutants == "Ultrafine Particles") %>%
#              mutate(Year = year(Date), Month = month(Date)) %>% 
#              mutate(DateTime = my(paste0(Month, '/', Year))) %>% 
#              group_by(Monitor, DateTime) %>% 
#              summarize(Avg = mean(Value, na.rm = TRUE)) %>%
#              ggplot(aes(x = Monitor, y = Avg, color = Monitor))+
#              geom_boxplot()+
#              labs(title = "Monthly Averages Between Monitors")+
#              theme(plot.title = element_text(hjust = 0.5)))

```

## {-}

## ELABHWC Black Carbon Plots {.tabset}

### Hourly Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
# Hourly averages
ggplotly(ELABHWC_merged %>% 
    filter(Pollutants == "Black Carbon") %>% 
    ggplot(aes(x = DateTime, y = Value, color = Monitor))+
    geom_line()+
    labs(x = "Date", title = "ELABHWC Hourly Averages for Black Carbon")+
    theme(plot.title = element_text(hjust = 0.5)))
```

### Daily Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
# Daily Averages
ggplotly(ELABHWC_merged %>% 
    filter(Pollutants == "Black Carbon") %>% 
    group_by(Monitor, Date) %>% 
    summarize(Avg = mean(Value), na.rm = TRUE) %>% 
    arrange(Date, .by_group = TRUE) %>% 
    ggplot(aes(x = Date, y = Avg, color = Monitor))+
    geom_line()+
    labs(x = "Date", title = "ELABHWC Daily Averages for Black Carbon")+
    theme(plot.title = element_text(hjust = 0.5)))
```

### Monthly Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
# Monthly Averages
ggplotly(ELABHWC_merged %>% 
             filter(Pollutants == "Black Carbon") %>%
             mutate(Year = year(Date), Month = month(Date)) %>% 
             mutate(DateTime = my(paste0(Month, '/', Year))) %>% 
             group_by(Monitor, DateTime) %>% 
             summarize(Avg = mean(Value, na.rm = TRUE)) %>%
             ggplot(aes(x = DateTime, y = Avg, color = Monitor))+
             geom_line()+
             labs(title = "ELABHWC Monthly Averages for Black Carbon")+
             theme(plot.title = element_text(hjust = 0.5)))

```

## {-}

## ELABHWC Ultrafine Particle Plots {.tabset}

### Hourly Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplotly(ELABHWC_merged %>% 
             filter(Pollutants == "Ultrafine Particles") %>% 
             ggplot(aes(x = DateTime, y = Value, color = Monitor))+
             geom_line()+
           scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                  labels = trans_format("log10", math_format(10^.x)))+
             labs(x = "Date", title = "ELABHWC Hourly Averages for Ultrafine Particles")+
             theme(plot.title = element_text(hjust = 0.5)))%>% 
  layout(yaxis = list(ticktext = c(TeX("$10^{0}$"), TeX("$10^{1}$"), TeX("$10^{2}$"), TeX("$10^{3}$"),
                                   TeX("$10^{4}$"), TeX("$10^{5}$")),
                        tickfont = list(size = 15))) %>%
    config(mathjax = "cdn")

```

### Daily Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplotly(ELABHWC_merged %>% 
             filter(Pollutants == "Ultrafine Particles") %>% 
             group_by(Monitor, Date) %>% 
             summarize(Avg = mean(Value), na.rm = TRUE) %>% 
             arrange(Date, .by_group = TRUE) %>% 
             ggplot(aes(x = Date, y = Avg, color = Monitor))+
             geom_line()+
           scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                  labels = trans_format("log10", math_format(10^.x)))+
           labs(x = "Date", title = "ELABHWC Daily Averages for Ultrafine Particles.")+
             theme(plot.title = element_text(hjust = 0.5)))%>% 
  layout(yaxis = list(ticktext = c(TeX("$10^{-1}$"), TeX("$10^{0}$"), TeX("$10^{1}$"), TeX("$10^{2}$"),
                                   TeX("$10^{3}$"), TeX("$10^{4}$")),
                        tickfont = list(size = 15))) %>%
    config(mathjax = "cdn")
```

### Monthly Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplotly(ELABHWC_merged %>% 
             filter(Pollutants == "Ultrafine Particles") %>%
             mutate(Year = year(Date), Month = month(Date)) %>% 
             mutate(DateTime = my(paste0(Month, '/', Year))) %>% 
             group_by(Monitor, DateTime) %>% 
             summarize(Avg = mean(Value, na.rm = TRUE)) %>%
             ggplot(aes(x = DateTime, y = Avg, color = Monitor))+
             geom_line()+
           scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                  labels = trans_format("log10", math_format(10^.x)))+
           labs(title = "ELABHWC Monthly Averages for Ultrafine Particles")+
             theme(plot.title = element_text(hjust = 0.5)))%>% 
  layout(yaxis = list(ticktext = c(TeX("$10^{4}$"), TeX("$10^{4.1}$"), TeX("$10^{4.2}$"), TeX("$10^{4.3}$"),
                                   TeX("$10^{4.4}$")),
                        tickfont = list(size = 15))) %>%
    config(mathjax = "cdn")

```

## {-}

## SELA Black Carbon Plots {.tabset}

### Hourly Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplotly(SELA %>% 
    filter(Pollutants == "Black Carbon") %>% 
    ggplot(aes(x = DateTime, y = Value, color = Monitor))+
    geom_line()+
    labs(x = "Date", title = "SELA Hourly Averages for Black Carbon")+
    theme(plot.title = element_text(hjust = 0.5)))
```

### Daily Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplotly(SELA %>% 
             filter(Pollutants == "Black Carbon") %>% 
             group_by(Monitor, Date) %>% 
             summarize(Avg = mean(Value), na.rm = TRUE) %>% 
             arrange(Date, .by_group = TRUE) %>% 
             ggplot(aes(x = Date, y = Avg, color = Monitor))+
             geom_line()+
             labs(x = "Date", title = "SELA Daily Averages for Black Carbon")+
             theme(plot.title = element_text(hjust = 0.5)))
```

### Monthly Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplotly(SELA %>% 
             filter(Pollutants == "Black Carbon") %>%
             mutate(Year = year(Date), Month = month(Date)) %>% 
             mutate(DateTime = my(paste0(Month, '/', Year))) %>% 
             group_by(Monitor, DateTime) %>% 
             summarize(Avg = mean(Value, na.rm = TRUE)) %>%
             ggplot(aes(x = DateTime, y = Avg, color = Monitor))+
             geom_line()+
             labs(title = "ELABHWC Monthly Averages for Black Carbon")+
             theme(plot.title = element_text(hjust = 0.5)))
```

## {-}

## SELA Ultrafine Particle Plots {.tabset}

### Hourly Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplotly(SELA %>% 
             filter(Pollutants == "Ultrafine Particles") %>% 
             ggplot(aes(x = DateTime, y = Value, color = Monitor))+
             geom_line()+
           scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                  labels = trans_format("log10", math_format(10^.x)))+
             labs(x = "Date", title = "SELA Hourly Averages for Ultrafine Particles")+
             theme(plot.title = element_text(hjust = 0.5))) %>% 
  layout(yaxis = list(ticktext = c(TeX("$10^{0}$"), TeX("$10^{1}$"), TeX("$10^{2}$"), TeX("$10^{3}$"),
                                   TeX("$10^{4}$"), TeX("$10^{5}$")),
                        tickfont = list(size = 15))) %>%
    config(mathjax = "cdn")
```


### Daily Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplotly(SELA %>% 
             filter(Pollutants == "Ultrafine Particles") %>% 
             group_by(Monitor, Date) %>% 
             summarize(Avg = mean(Value), na.rm = TRUE) %>% 
             arrange(Date, .by_group = TRUE) %>% 
             ggplot(aes(x = Date, y = Avg, color = Monitor))+
             geom_line()+
           scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                  labels = trans_format("log10", math_format(10^.x)))+
           labs(x = "Date", title = "SELA Daily Averages for Ultrafine Particles")+
             theme(plot.title = element_text(hjust = 0.5))) %>% 
  layout(yaxis = list(ticktext = c(TeX("$10^{3.8}$"), TeX("$10^{4}$"), TeX("$10^{4.2}$"), TeX("$10^{4.4}$")),
                        tickfont = list(size = 15))) %>%
    config(mathjax = "cdn")
```

### Monthly Averages
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplotly(SELA %>% 
             filter(Pollutants == "Ultrafine Particles") %>%
             mutate(Year = year(Date), Month = month(Date)) %>% 
             mutate(DateTime = my(paste0(Month, '/', Year))) %>% 
             group_by(Monitor, DateTime) %>% 
             summarize(Avg = mean(Value, na.rm = TRUE)) %>%
             ggplot(aes(x = DateTime, y = Avg, color = Monitor))+
             geom_line()+
           scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                  labels = trans_format("log10", math_format(10^.x)))+
           labs(title = "ELABHWC Monthly Averages for Ultrafine Particles")+
             theme(plot.title = element_text(hjust = 0.5))) %>% 
  layout(yaxis = list(ticktext = c(TeX("$10^{4.1}$"), TeX("$10^{4.15}$"), TeX("$10^{4.2}$"), TeX("$10^{4.25}$"),
                                   TeX("$10^{4.3}$"), TeX("$10^{4.35}$")),
                        tickfont = list(size = 15))) %>%
    config(mathjax = "cdn")

```

## {-}

